### 2022-04-14 response_reviewers.tex

    Conscious and unconscious bias can also operate when the submitted work is not written, but rather in video form. We added a short mention and citation about how video abstracts can be exclusionary (Spitschan et al 2021) by adding barriers to people with visible disabilities, diverse body types, non-native language speakers, or less resources to create videos (lines \ref{video-1} to \ref{video-2}).
    We thank the reviewer for this comment that led us to the current addition.
\end{Reply}

@@

6. In Rule 8, inclusive communication strategy - it is important that the speakers from diverse backgrounds, especially from ethnic minorities etc are highlighted or given prominence in social media strategy or communication. Often, these speakers face relatively less focus. This may be discussed.

\begin{Reply}
    We added the following text to the manuscript (lines \ref{promotion-1} to \ref{promotion-2}): 
    \textit{During the conference, pay special attention to promoting the sessions led, chaired, and presented by people in minoritized groups, multilingual sessions, and the diversified thematic sessions (see \textbf{Rule 4}) to give them the same visibility than all other sessions.}
\end{Reply}

7. In Conclusion, suggest also adding that issues of diversity and inclusion have come to fore even more during COVID-19 as we witness exacerbation of inequities disadvantaging those from vulnerable backgrounds (see https://pubmed.ncbi.nlm.nih.gov/33343410/PMID: 33343410)

\begin{Reply}
% RJ: I'm leaning towards not adding this now.
    We appreciate the suggestion and agree that the COVID-19 pandemic contributed to the exacerbation of inequity. 
    However, we would like the manuscript to help inspire and guide the organization of more inclusive conferences regardless of the state of the pandemic in the different places in the world, and even when the pandemic subsides. For that reason, we tried to mention the pandemic very few times and only when deemed necessary: to give context to the conference that we organized, and to talk about virtual conferences which became the prevailing format during the last two years.  
\end{Reply}

\begin{Reply}
    We thank the reviewer for their comments and careful revision.
\end{Reply}
